---
title: "Customer Overview Report"
date: "12/3/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
library(tidyverse)
library(corrplot)
library(ggpubr)

options( scipen = 999 )

raw_data <- read.csv(file = 'training set.csv')

#Handle missing Value in Product Columns
#Input 0 if it is NA in Product Columns
raw_data[, 25:48][is.na(raw_data[, 25:48])] <- 0

#Check missing value
#raw_data %>% select(everything()) %>% summarise_all(funs(sum(is.na(.))))

#Rename product columns
colnames(raw_data)<-c('Record_Date','Customer_id','Employee_Index','Country_Residence','Gender','Age','First_Contract_Date','New_Customer_Index','Customer_Seniority','Primary_Customer_Index','Primary_Customer_LastDate','CustomerType','RelationType','Residence_Index','Foreigner_Index','Spouse_Index','Channel','Decrease_Index','Address_Type','Province_Code','Province_Name','Activity_Index','Gross_Income','Segmentation_Index','Saving_acc','Guarantees','Current_acc','Derivada_acc','Payroll_acc','Junior_acc','MasParticular_acc','Particular_acc','ParticularPlus_acc','ShortTermDeposit','MediumTermDeposit','LongTermDeposit','E_acc','Funds','Mortgage','Pensions1','Loans','Taxes','Credit_Card','Securities','Home_acc','Payroll','Pensions2','Direct_Debit')

#Update age field (change string to numeric, NA to 0)
raw_data$Age <- as.numeric(raw_data$Age) 
raw_data$Age[is.na(raw_data$Age)] <- 0

#Add new fields
AdjRawData<-raw_data %>% 
  filter(Age!=0)%>%
  filter(Segmentation_Index!="") %>%
  mutate(Product_Count = rowSums(.[25:48])) %>% 
  mutate(Age_Range = ifelse(Age<=20,"20 or below",
                      ifelse(Age<31,"21-30",
                      ifelse(Age<41,"31-40",
                      ifelse(Age<51,"41-50",
                      ifelse(Age<61,"51-60",
                      ifelse(Age>60,"Over 60","Others")))))))%>%
  mutate(Sex = ifelse(Gender=="H","Male",
                      ifelse(Gender=="V","Female","Others")))

#Gross Income: Change NA to 0
AdjRawData$Gross_Income[is.na(AdjRawData$Gross_Income)] <- 0

```

## Customer Insights Analytics

### 1. Product Correlation
####Statistics of Product Number Purchased by Customer

```{r, echo=FALSE}
#Stat of Product Count
summary(AdjRawData$Product_Count)
```

####Relationship Among Product

```{r, echo=FALSE}
#############Product Purchase Association#############
#Graph: Correlation between product
Product_Corr = cor(raw_data[, 25:48])
corrplot(Product_Corr, type="upper", order="hclust")
```

### 2. Age
####Statistics of Customer Age

```{r, echo=FALSE}
#############Age#############
#Stat of Age
summary(raw_data$Age)
```

####Age Distribution

```{r, echo=FALSE}
#Graph: Distribution of Age
AdjRawData %>%
  filter(Gender%in%c("H","V")) %>%
  ggplot(aes(x=Age))+geom_bar()+ 
  ggtitle("Distribution of Customer's Age") +
  xlab("Age") + ylab("Count")
```

####Average Number of Product per Age

```{r, echo=FALSE}
#Graph: Average Product Count per Age
AdjRawData %>%
  group_by(Age_Range) %>%
  summarise_at(vars(Product_Count), list(Average_Product_No = mean)) %>%
  ggplot(aes(x=Age_Range, y=Average_Product_No, label =round(Average_Product_No,2)))+ 
  geom_bar(stat="identity")+ geom_label(vjust = -0.1) + 
  ggtitle("Average Number of Product per Age Range") +
  xlab("Age") + ylab("Average Number of Product")
```

####Total Number of Product per Age

```{r, echo=FALSE}
#Graph: Sum of Product Number per Date (Each Age Group)
AdjRawData %>%
  group_by(Record_Date,Age_Range) %>%
  summarise_at(vars(Product_Count), list(Total_Product_No = sum)) %>%
  ggplot(aes(x=Record_Date, y=Total_Product_No, group = 1))+ 
  geom_line(size = 1) +
  geom_point() +
  ggtitle("Total Number of Product per Age Range") +
  xlab("Date") + ylab("Total Number of Product")+ 
  facet_wrap(. ~ Age_Range) + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

### 3. Gender
####Statistics of Customer Gender

```{r, echo=FALSE}
#############Gender#############
#Stat
AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Product_Count), list(Total_Product_No = sum))
```

####Gender Distribution

```{r, echo=FALSE}
#Graph: Gender pie chart (total)
AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Product_Count), list(Total_Product_No = sum)) %>%
  ggplot(aes(x="", y=Total_Product_No, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0)+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("")  +
  ggtitle("Total Number of Product")
```

####Age Distribution in Each Product

```{r, echo=FALSE}
#Graph: Gender pie chart (each product)

ProductName <- c('Saving_acc','Guarantees','Current_acc','Derivada_acc','Payroll_acc','Junior_acc','MasParticular_acc','Particular_acc','ParticularPlus_acc','ShortTermDeposit','MediumTermDeposit','LongTermDeposit','E_acc','Funds','Mortgage','Pensions1','Loans','Taxes','Credit_Card','Securities','Home_acc','Payroll','Pensions2','Direct_Debit')

Pie1 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Saving_acc), list(Total_Saving_acc = sum)) %>%
  ggplot(aes(x="", y=Total_Saving_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie2 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Guarantees), list(Total_Guarantees = sum)) %>%
  ggplot(aes(x="", y=Total_Guarantees, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie3 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Current_acc), list(Total_Current_acc = sum)) %>%
  ggplot(aes(x="", y=Total_Current_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie4 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Derivada_acc), list(Total_Derivada_acc = sum)) %>%
  ggplot(aes(x="", y=Total_Derivada_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie5 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Payroll_acc), list(Total_Payroll_acc = sum)) %>%
  ggplot(aes(x="", y=Total_Payroll_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie6 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Junior_acc), list(Total_Junior_acc = sum)) %>%
  ggplot(aes(x="", y=Total_Junior_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie7 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(MasParticular_acc), list(Total_MasParticular_acc = sum)) %>%
  ggplot(aes(x="", y=Total_MasParticular_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie8 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Particular_acc), list(Total_Particular_acc = sum)) %>%
  ggplot(aes(x="", y=Total_Particular_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie9 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(ParticularPlus_acc), list(Total_ParticularPlus_acc = sum)) %>%
  ggplot(aes(x="", y=Total_ParticularPlus_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie10 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(ShortTermDeposit), list(Total_ShortTermDeposit = sum)) %>%
  ggplot(aes(x="", y=Total_ShortTermDeposit, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie11 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(MediumTermDeposit), list(Total_MediumTermDeposit = sum)) %>%
  ggplot(aes(x="", y=Total_MediumTermDeposit, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie12 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(LongTermDeposit), list(Total_LongTermDeposit = sum)) %>%
  ggplot(aes(x="", y=Total_LongTermDeposit, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie13 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(E_acc), list(Total_E_acc = sum)) %>%
  ggplot(aes(x="", y=Total_E_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie14 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Funds), list(Total_Funds = sum)) %>%
  ggplot(aes(x="", y=Total_Funds, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie15 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Mortgage), list(Total_Mortgage = sum)) %>%
  ggplot(aes(x="", y=Total_Mortgage, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie16 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Pensions1), list(Total_Pensions1 = sum)) %>%
  ggplot(aes(x="", y=Total_Pensions1, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie17 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Loans), list(Total_Loans = sum)) %>%
  ggplot(aes(x="", y=Total_Loans, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie18 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Taxes), list(Total_Taxes = sum)) %>%
  ggplot(aes(x="", y=Total_Taxes, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie19 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Credit_Card), list(Total_Credit_Card = sum)) %>%
  ggplot(aes(x="", y=Total_Credit_Card, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie20 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Securities), list(Total_Securities = sum)) %>%
  ggplot(aes(x="", y=Total_Securities, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie21 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Home_acc), list(Total_Home_acc = sum)) %>%
  ggplot(aes(x="", y=Total_Home_acc, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie22 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Payroll), list(Total_Payroll = sum)) %>%
  ggplot(aes(x="", y=Total_Payroll, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie23 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Pensions2), list(Total_Pensions2 = sum)) %>%
  ggplot(aes(x="", y=Total_Pensions2, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

Pie24 <- AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Sex) %>%
  summarise_at(vars(Direct_Debit), list(Total_Direct_Debit = sum)) %>%
  ggplot(aes(x="", y=Total_Direct_Debit, fill=Sex)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start=0) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank()) +
  xlab("") + ylab("") 

ggarrange(Pie1,Pie2,Pie3,Pie4,Pie5,Pie6,Pie7,Pie8,Pie9,Pie10,Pie11,Pie12,Pie13,Pie14,Pie15,Pie16,Pie17,Pie18,Pie19,Pie20,Pie21,Pie22,Pie23,Pie24 + rremove("x.text"),
          labels = c('Saving_acc','Guarantees','Current_acc','Derivada_acc','Payroll_acc','Junior_acc','MasParticular_acc','Particular_acc','ParticularPlus_acc','ShortTermDeposit','MediumTermDeposit','LongTermDeposit','E_acc','Funds','Mortgage','Pensions1','Loans','Taxes','Credit_Card','Securities','Home_acc','Payroll','Pensions2','Direct_Debit'),
          ncol = 4,nrow = 6,
          font.label=list(size=8),
          vjust=0)+
          theme(plot.margin = margin(0.2,0.2,2,0.2,"cm"))
```

####Total Number of Product per Gender

```{r, echo=FALSE}
#Graph: Sum of Product Number per Date (Each Gender)
AdjRawData %>%
  filter(Sex%in%c("Male","Female"))%>%
  group_by(Record_Date,Sex) %>%
  summarise_at(vars(Product_Count), list(Total_Product_No = sum)) %>%
  ggplot(aes(x=Record_Date, y=Total_Product_No, group = 1))+ 
  geom_line(size = 1) +
  geom_point() +
  ggtitle("Total Number of Product") +
  xlab("Date") + ylab("Total Number of Product per Gender") +
  facet_wrap(.~Sex)+ theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

### 4. Gross Income
####Statistics of Customer Gross Income

```{r, echo=FALSE}
#############Gross Income#############
#Stat of Gross Income
summary(AdjRawData$Gross_Income)
```

####Average Number of Product versus Gross Income

```{r, echo=FALSE}
#Graph: Average of Product Number per Gross Income 
AdjRawData %>%
  filter(Gross_Income>0) %>%
  ggplot(aes(x=Gross_Income, y=Product_Count)) + 
  geom_point(alpha = 0.3) + 
  ggtitle("Average Number of Product per Gross Income") +
  xlab("Gross Income") + ylab("Average Number of Product")
```

### 5. Customer Type
####Statistics of Customer Type

```{r, echo=FALSE}
#############Segmentation#############
#Stat of Segmentation
AdjRawData %>%
  ggplot(aes(x=Segmentation_Index)) + geom_bar()+ 
  ggtitle("Total Number of Customer Type") +
  xlab("Customer Type") + ylab("Total Number of Product")
```

####Total Number of Product per Customer Type

```{r, echo=FALSE}
#Graph: Total product number per segmentation
Pie25 <- AdjRawData %>%
  filter(Segmentation_Index=="01 - TOP") %>%
  filter(Sex %in% c("Male","Female")) %>%
  group_by(Record_Date,Sex) %>%
  summarise_at(vars(Product_Count), list(Total_Product_No = sum)) %>%
  ggplot(aes(x=Record_Date, y=Total_Product_No, group = 1,color=Sex))+ 
  geom_point() + theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  xlab("") + ylab("")

Pie26 <- AdjRawData %>%
  filter(Segmentation_Index=="02 - PARTICULARES") %>%
  filter(Sex %in% c("Male","Female")) %>%
  group_by(Record_Date,Sex) %>%
  summarise_at(vars(Product_Count), list(Total_Product_No = sum)) %>%
  ggplot(aes(x=Record_Date, y=Total_Product_No, group = 1,color=Sex))+ 
  geom_point() + theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  xlab("") + ylab("")

Pie27 <- AdjRawData %>%
  filter(Segmentation_Index=="03 - UNIVERSITARIO") %>%
  filter(Sex %in% c("Male","Female")) %>%
  group_by(Record_Date,Sex) %>%
  summarise_at(vars(Product_Count), list(Total_Product_No = sum)) %>%
  ggplot(aes(x=Record_Date, y=Total_Product_No, group = 1,color=Sex))+ 
  geom_point() + theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  xlab("") + ylab("")

plot <- ggarrange(Pie25,Pie26,Pie27,
          labels = c('VIP','Individuals','College graduated'),
          ncol = 2,nrow = 2,
          font.label=list(size=8),
          vjust=0)+
          theme(plot.margin = margin(0.2,0.2,2,0.2,"cm"))

annotate_figure(plot, top = text_grob("Total Number of Product", face = "bold", size = 14))
```

####Range of Product Number per Customer Type

```{r, echo=FALSE}
#Graph: Boxplot (product count) (total)
AdjRawData %>%
  ggplot(aes(x=Segmentation_Index,y=Product_Count)) + geom_boxplot()+
  xlab("Customer Type") + ylab("Total Number of Product")
```
